Chemical tagging can work: \\ Identification of stellar phase-space structures \\ purely by chemical-abundance similarity

### 2016-01-17 papers/clusters.tex
small tweaks of HWR stuff

% to-do
% - write data and cannon section
% - write method and results section
% - write discussion section
% - put in references
% - cite codes!
% - fix all remaining occurrences of ARC, MKN, HWR, DWH, or CITE
% - forward to Freeman, others?
% - submit to journal and arXiv

@@

Ensembles of stars in the Milky Way are born in molecular clouds,
which are presumed to be near-homogeneous in their chemical element composition.
However, most stars are born in unbound associations, or are born in star clusters that disperse rapidly: they will eventually end up in very different parts of phase space, on differing orbits.
Yet, if every star preserved its photospheric element abundances over its lifetime (at least for most elements), then stars of common birth origin ought to be identifiable through their detailed photospheric abundances, long after any spatial or phase-space proximity has vanished.

@@

Although undeniably promising---and motivating the 
launch of costly large-scale spectroscopic surveys---
chemical-tagging as a search technique has yet to be proven in practice: identifying stars of common birth origin {\it purely} on the basis of their near-identical abundances patterns, without any consideration of position or velocity.

@@

\section{Data: \apogee\  giants with [X/H] re-derived from \thecannon }

Our analysis draws on the spectra of \totalnumber\ giant stars ($\logg < 3.9$) from \apogee\ \acronym{DR12} (\cite{dr12}), alll those not flagged as bad in the \apogee\ \aspcap\ (\cite{aspcap}) pipeline reductions. We re-analyze these
\emph{spectra} using \thecannon\ , because this deliver stellar abundance labels of higher precision, especially for stars of SNR$\le 150$.

The details about how we select, reduce, and analyze the \apogee\ data are given in full detail in the companion papers \citep{casey16, ness16}, and we only summarize briefly here.
We re-derived 17 labels ($\teff$, $\logg$, and 15 abundances
referenced to H) form the \apogee\ \acronym{DR12} spectra. 
In the \thecannon 's  training step we trained on the
ARC:XXXXX red-giant stars that have spectral SNR$\ge 200$.
For this small fraction of the sample with the highest SNR objects the labels provided by \aspcap provide consistent, low-scatter,
sensible abundance-space measurements. The training step fixes a spectral model that predics the normalized spectrum as a quadratic function of all labels. In the second stage---the test step---each unlabeled star is used to establish a single-star likelihood function for its labels, holding the model
coefficients fixed.
\thecannon\ finds the labels that minimize the single-star likelihood
function for each test-set star.
This optimization is not convex, but it is embarrassingly parallel,
and therefore fast. The test
step takes less than an hour on a small research cluster in Cambridge.

@@

\clearpage
\section{Method and results}\label{sec:method}

>>>>

% to-do
% - write discussion section w MKN input
% - expand kmeans discussion
% - put in references
% - cite codes!
% - fix all remaining occurrences of ARC, MKN, HWR, DWH, or CITE
% - forward to Freeman, others?
% - submit to journal and arXiv

% style notes
% - never use \cite{}, always \citep{} or \citealt{}.

@@

Ensembles of stars in the Milky Way are born in molecular clouds,
which are presumed to be near-homogeneous in their chemical element
composition.
However, most stars are born in unbound associations, or are born in
star clusters that disperse rapidly; they will eventually end up in
very different parts of phase space, on differing orbits.
Yet, if every star preserved its photospheric element abundances over
its lifetime (at least for most elements), then stars of common birth
origin ought to be identifiable through their detailed photospheric
abundances, long after any spatial or phase-space proximity has
vanished.

@@

Although undeniably promising---and motivating the 
launch of costly large-scale spectroscopic surveys---%
chemical-tagging as a search technique has yet to be proven in
practice: identifying stars of common birth origin {\it purely} on the
basis of their near-identical abundances patterns, without any
consideration of position or velocity.

@@

\section{Data: \apogee\ giants with abundances from \thecannon}\label{sec:data}

Our analysis draws on the spectra of \totalnumber\ giant stars ($\logg
< 3.9$) from \apogee\ \acronym{DR12} \citep{dr12}, alll those not
flagged as bad in the \apogee\ \aspcap\ \citep{aspcap} pipeline
reductions.
We re-analyze these \emph{spectra} using \thecannon, because this
deliver stellar abundance labels of higher precision, especially for
stars of SNR$\le 150$.
The details about how we select, reduce, and analyze the \apogee\ data
are given in full detail in the companion papers \citep{casey16,
  ness16}, and we only summarize briefly here.
We re-derived 17 labels ($\teff$, $\logg$, and 15 abundances
referenced to H) form the \apogee\ \acronym{DR12} spectra. 
For the training step of \thecannon, 
ARC:XXXXX red-giant stars with spectral SNR$\ge 200$ were used.
For this small fraction of the sample with the highest SNR objects the
labels provided by \aspcap provide consistent, relatively low-scatter, sensible
abundance-space measurements.
The training step fixes a spectral model
that predics the normalized spectrum as a quadratic function of all
labels. In the second stage---the test step---each unlabeled star is
used to establish a single-star likelihood function for its labels,
holding the model coefficients fixed.
\thecannon\ finds the labels that minimize the single-star likelihood
function for each test-set star.
This optimization is not convex, but it is embarrassingly parallel,
and therefore fast. The test
step takes less than an hour on a small research cluster in Cambridge.

% HWR commented this (below) out

@@

\clearpage
\section{Clustering method and results}\label{sec:method}
